Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-12 paper.tex
Address todo item regarding experimental results

\caption{Reynolds number dependence of the normalized peak torque coefficient
calculated from static foil coefficients and blade kinematics, compared to
experimental data from a cross-flow turbine.}

@@

\todo[inline]{Is this the peak torque coefficient or the mean power coefficient?}

>>>>

\caption{Reynolds number dependence of the normalized peak torque coefficient
    calculated from static foil coefficients and blade kinematics, compared to
    experimental data from a cross-flow turbine. Note that the experimental data
    represents the mean torque coefficient, not the maximum.}

@@
